Verifying Demonstrations

### 2019-09-06 paper/DB-anon-cred.tex
Fix typo in comment: DH -> DBDH acronym
Adds minor text before TF proof.
Adds Bussard-Bagga where relevant

We will now introduce \iac{DB} protocol which is a \ac{ZKPK} for discrete 
logarithms.
Our protocol is an adaptation of the Schnorr identification 
scheme~\cite{Schnorr}, albeit different from that of 
\textcite{DistanceBounding} in the original \ac{DB} paper.
(That protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
terrorist fraud.)
We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
protocol which is \iac{ZKPK} that is secure against \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBTF}.
This yields strong privacy properties and protection against a malicious, 
impersonating verifier.

@@

  \daniel{\Ac{DH} is kind of adaptive and concurrent \ac{ZKPK}, I must read up 
    on that (there is a paper by Bellare).}
\end{proof}

>>>>

We will now introduce \iac{DB} protocol which is a \ac{ZKPK} for discrete 
logarithms.
Our protocol is an adaptation of the Schnorr identification 
scheme~\cite{Schnorr}, albeit different from that of 
\textcite{DistanceBounding} in the original \ac{DB} paper\footnote{%
  The \citeauthor{DistanceBounding} protocol was shown to be prone to distance 
  hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
  terrorist fraud.
} and that of \textcite{Bussard-Bagga}\footnote{%
  The \citeauthor{Bussard-Bagga} protocol was also shown to be 
  vulnerable~\cite{Bussard-Bagga-attack}.
  Although this time, the protocol could not protect against \ac{DBTF} and 
  \ac{DBDF} as it claimed.
}.
We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
protocol which is \iac{ZKPK} that is secure against \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBTF}.
This yields strong privacy properties and protection against a malicious, 
impersonating verifier.

@@

  \daniel{\Ac{DBDH} is kind of adaptive and concurrent \ac{ZKPK}, I must read 
    up on that (there is a paper by Bellare).}
\end{proof}

The last property is \ac{DBTF}.

### 2019-09-06 paper/intro.tex
Adds Bussard-Bagga where relevant

%\emph{Context.}

@@

Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attack against the original protocol of 
Brands and Chaum) and \ac{DBTF}.
More importantly, it is public-key, handles malicious impersonating verifiers.
Since it is based on the Schnorr protocol, it provides a distance-bounded 
\ac{PK} for discrete logarithms.
That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
distance-bounding version and thus make general privacy-preserving, 
attribute-based credential systems distance bounding.

>>>>

@@

Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding} or 
\textcite{Bussard-Bagga} (DBPK-Log).
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attack against the original protocol of 
Brands and Chaum) and \ac{DBTF}.
More importantly, it is public-key\footnote{%
  The majority of published works are in the shared-key setting.
  However, both the protocol by \textcite{DistanceBounding} and that of 
  \textcite{Bussard-Bagga} are public key.
}, handles malicious impersonating verifiers.
Since it is based on the Schnorr protocol, it provides a distance-bounded 
\ac{PK} for discrete logarithms.
That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
distance-bounding version and thus make general privacy-preserving, 
attribute-based credential systems distance bounding.
